### 2020-05-15 writeup/transfer.tex
3.2

\subsection{Task Model Similarities}

@@

\textbf{Example.}
	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
	For the task models, suppose that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ also has i.i.d. entries with mean $0$ and variance $d^2$.
	We have $n_i = c_i \cdot p$ data points from each task, for $i = 1, 2$.

@@

Specifically, the transition threshold is derived in the following proposition.
\begin{proposition}\label{prop_dist_transition}
	In the example described above, assume that $c > 100$ is a fixed constant.
	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
	\begin{itemize}
		\item If ${p\cdot d^2}/{\sigma^2} < \frac 2 3 \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If ${p\cdot d^2}/{\sigma^2} \ge \frac 3 2 \frac{(c_1 + c_2 -1)^2}{c_1(c_1 + c_2)(c_2 - 1)} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}

@@

@@

\subsection{Data Efficiency}

>>>>

\subsection{Task Model Similarities versus Noise}

@@

\begin{example}\label{ex_basic}
	Consider a setting where $\Sigma_1 = \Sigma_2 = \id$, in other words there is no covariate shift between the two tasks.
	For the task models, suppose that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ also has i.i.d. entries with mean $0$ and variance $d^2$.
	We have $n_i = c_i \cdot p$ data points from each task, for $i = 1, 2$.
\end{example}

@@

Specifically, the transition threshold is derived in the following proposition.
\begin{proposition}\label{prop_dist_transition}
	In the setting of Example \ref{ex_basic}, assume that $c > 100$ is a fixed constant.
	Whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$ is determined by the ratio between the model distance and the noise level:
	\begin{itemize}
		\item If ${d^2} < \frac {2\sigma^2} {3p} \frac{(c_1 + c_2 -1)^2}{c_1 (c_1 + c_2)(c_2 - 1)} - o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
		\item If ${d^2} \ge \frac {3\sigma^2} {2p} \frac{(c_1 + c_2 -1)^2}{c_1(c_1 + c_2)(c_2 - 1)} + o(1)$, then whp we have that $\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})$.
	\end{itemize}
\end{proposition}

@@

\begin{example} \todo{Add transfer from low accuracy to high accuracy}
\end{example}

@@

\subsection{Data Size and Efficiency}

In classical Rademacher or VC based theory of multi-task learning, adding more labeled data improves the generalization performance of a model.
On the other hand, we have observed that adding more labeled data does not always improve performance in multi-task learning.
Using Example \ref{ex_basic}, we analyze the effect of varying the source task data size.

\begin{proposition}\label{prop_data_size}
	In the setting of Example \ref{ex_basic}, assume that $c_1 > ??$ and $c_2  > ??$ are fixed constants.
	We have the following conditions to determine whether $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$:
	\begin{itemize}
		\item If $d^2 < \frac{\sigma^2}{(c_2 - 1) p}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$, for any $c_1$ larger than $??$.
		\item If $d^2 > \frac{\sigma^2}{(c_2 - 1) p}$, then we have the following transition depending on $c_1$:
		\begin{itemize}
			\item If $?? < c_1 < \frac{c_2 \sigma^2}{(c_2 - 1) pd^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) < \te(\hat{\beta}_t^{\STL})$.
			\item If $c_1 > \frac{c_2 \sigma^2}{(c_2 - 1)p d^2 - \sigma^2}$, then whp $\te(\hat{\beta}_t^{\MTL}) > \te(\hat{\beta}_t^{\STL})$.
		\end{itemize}
	\end{itemize}
	Furthermore, as a function of $c_1$ over the range $[??, \infty]$, the maximum of $\te(\hat{\beta}_t^{\STL}) - \te(\hat{\beta}_t^{\MTL})$ is attained when $c_1 = {c_2\sigma^2}/{\max(2(c_2 - 1)pd^2 -\sigma^2, 0)}$.
\end{proposition}
